A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-23 doc/paper.tex
More user study. Fixes #78, fixes #79, fixes #80.

	\section{User Study} During development, we conducted a brief, four-participant
	user study in order to detect conflicts between our design and the goals in
	section \ref{goals}. We designed the study to be exploratory; given trees based
	in the Enron dataset and at least twenty minutes, we asked the participants to
	adopt the persona of a consultant evaluating a company's spreadsheet
	practice, allowing for questions like which functions on which the employees
	most depended or which sheets or employees presented the most anomalous or
	dangerous designs. Though we instructed them on how to use the tool and
	suggested that they visit one of the most populous trees in the set, we put
	aside any specific tasks or questions and let them choose their own paths.
	Though interpretation of the phrase ``spreadsheet practice" can certainly vary
	from participant to participant, we readily accepted this interpretive
	flexibility since we wanted a range of views and backgrounds despite the
	persona. \par

	We clarified, furthermore, that these notes could be directed either at the
	quality of the data conveyed by the tool or at the tool's conveyance itself.
	Since the tool's philosophy was based in exploration, we decided that it would
	not have been appropriate to restrict what people were to look for, letting
	them find interesting stories of formula construction for themselves.
	Additionally, either kind of comment -- on data or on tool -- would direct us
	back to the central evaluation; a user's silence, or lack of any interesting
	findings, would tacitly indicate that perhaps the tool does not convey
	information well enough. \par

>>>>

	\section{User Study} During development, we conducted a brief, four-participant
	user study in order to detect conflicts between our design and the goals in
	section \ref{goals}. We designed the study to be exploratory; given trees based
	in the Enron dataset and at least twenty minutes, we asked the participants to
	adopt the persona of a consultant evaluating a company's spreadsheet
	practice, allowing for questions like which functions on which the employees
	most depended or which sheets or employees presented the most anomalous or
	dangerous designs. Though we instructed them on how to use the tool and
	suggested that they visit one of the most populous trees in the set, we put
	aside any specific tasks or questions and let them choose their own paths.
	Though interpretation of the phrase ``spreadsheet practice" can certainly vary
	from participant to participant, we readily accepted this interpretive
	flexibility since we wanted a range of views and backgrounds despite the
	persona. We clarified, furthermore, that their observations could be directed either at the
	quality of the data conveyed by the tool or at the tool's design itself. \par
